Models of lens candidates from Space Warps CFHTLS

### 2016-09-13 paper2-unstable.tex
rearranging figures

>>>>

\def\pwidth{.32\linewidth}

\def\includeten#1#2{
\includegraphics[width=\pwidth]{#1ASW0007k4r_N7LTELSYTM#2}%
\includegraphics[width=\pwidth]{#1ASW00096rm_4Q3YCEWGLN#2}%
\includegraphics[width=\pwidth]{#1ASW0007xrs_JHC3J2HYV7#2}\\
\includegraphics[width=\pwidth]{#1ASW0007iwp_4XBJWT3COV#2}%
\includegraphics[width=\pwidth]{#1ASW000619d_011489#2}%
\includegraphics[width=\pwidth]{#1ASW0001ld7_OS3CYAKLRT#2}\\
\includegraphics[width=\pwidth]{#1ASW0002asp_5EKMWWVJHL#2}%
%\includegraphics[width=\pwidth]{#1ASW000096t_7IPP7LWVOF#2}%
\includegraphics[width=\pwidth]{#1ASW0008qsm_TOFS7JNGEK#2}%
\includegraphics[width=\pwidth]{#1ASW0008pag_5SXGXQYY6V#2}\\
}

\def\includezehn#1#2{
\includegraphics[width=\pwidth]{#1SW05_ASW0007k4r_N7LTELSYTM#2}%
\includegraphics[width=\pwidth]{#1SW42_ASW00096rm_4Q3YCEWGLN#2}%
\includegraphics[width=\pwidth]{#1SW28_ASW0007xrs_JHC3J2HYV7#2}\\
\includegraphics[width=\pwidth]{#1SW58_ASW0007iwp_4XBJWT3COV#2}%
\includegraphics[width=\pwidth]{#1SW02_ASW000619d_011489#2}%
\includegraphics[width=\pwidth]{#1SW19_ASW0001ld7_OS3CYAKLRT#2}\\
\includegraphics[width=\pwidth]{#1SW09_ASW0002asp_5EKMWWVJHL#2}%
%\includegraphics[width=\pwidth]{#1SW36_ASW000096t_7IPP7LWVOF#2}\\
\includegraphics[width=\pwidth]{#1SW29_ASW0008qsm_TOFS7JNGEK#2}%
\includegraphics[width=\pwidth]{#1SW57_ASW0008pag_5SXGXQYY6V#2}\\
}

\begin{figure*}
\includeten{spaghetti/}{_input}
\caption{}
\end{figure*}

%\begin{figure*}
%\includeten{spaghetti/}{_nsynth}
%\caption{}
%\end{figure*}

\begin{figure*}
\includezehn{img/arrival_spaghetti/}{_arrival_spaghetti}
\caption{}
\end{figure*}

\begin{figure*}
\includezehn{img/kappa_map/}{_kappa_map}
\caption{}
\end{figure*}

\begin{figure*}
\includezehn{img/kappa_encl/}{_kappa_encl}
\caption{}
\end{figure*}

\begin{figure*}
\includezehn{img/mlens_vs_mstel/}{_mstel_vs_mtot}
\caption{}
\end{figure*}

\end{document}

\end{document}
